\documentclass[fleqn]{article}
\pagenumbering{gobble}
\usepackage{amsmath}

\begin{document}
\subsection*{Definitions}
\noindent
The problem of finding a rate of change from other known rates of change is called a \textbf{related rates problem}.
\newline

\subsubsection*{Related Rates Problem Strategy}
\noindent
To solve a related rates problem, follow these steps:
\begin{itemize}
\item Draw a picture and name the variables and constants.
\item Write down the numerical information.
\item Write down what you are asked to find.
\item Write an equation that relates the variables.
\item Differentiate with respect to $t$.
\item Evaluate.
\end{itemize}

\subsection*{Example 1}
\noindent
Water runs into a canonical tank at the rate of $9 {ft}^3/min$. The tank stands point down and has a height of $10 ft$ and a base radius of $5 ft$. How fast is the water level rising when the water is $6 ft$ deep?

\begin{align*}
    y &= 6 ft \\
    \frac{dV}{dt} &= 9 {ft}^3/min
\end{align*}

\noindent
The water forms a cone with volume
\begin{equation*}
    V = \frac{1}{3} \pi x^2 y
\end{equation*}

\noindent
This equation involves $x$ as well as $V$ and $y$. Because no information is given about $x$ and $dx/dt$ at the time in equation, we need to eliminate $x$.

\begin{align*}
    \frac{x}{y} =& \frac{5}{10} \\
    x =& \frac{y}{2}
\end{align*}

\noindent
Therefore, we find

\begin{equation*}
    V = \frac{1}{3} \pi \left(\frac{y}{2}\right)^2 y = \frac{\pi}{12} y^3
\end{equation*}

\noindent
To give the derivative and then evaluate

\begin{align*}
    \frac{dV}{dt} =& \frac{\pi}{12}.3y^3 \frac{dy}{dt} = \frac{\pi}{4}y^2\frac{dy}{dt} \\
    9 =& \frac{\pi}{4}\left(6\right)^2\frac{dy}{dt} \\
    \frac{dy}{dt} =& \frac{1}{\pi} \approx 0.32
\end{align*}

\noindent
At the moment in question, the water level is rising approximately $0.32 ft/min$.

\subsection*{Exercises}
\noindent
Evaluate the rate of change in each of the following exercises:
\newline

\begin{enumerate}
\item Assume that $y = 5x$ and $dx/dt = 2$. Find $dy/dt$.
\item Assume that $2x + 3y = 12$ and $dy/dt = -2$. Find $dx/dt$.
\item If $y=x^2$ and $dx/dt=3$, then what is $dy/dt$ when $x=-1$?
\item If $x=y^3-y$ and $dy/dt=5$, then what is $dx/dt$ when $y=2$?
\item If $x^2+y^2=25$ and $dx/dt=-2$, then what is $dy/dt$ when $x=3$ and $y=-4$?
\item If $x^2y^3=4/27$ and $dy/dt=1/2$, then what is $dx/dt$ when $x=2$?
\item If $L=\sqrt{x^2+y^2}$, $dx/dt=-1$, and $dy/dt=3$, find $dL/dt$ when $x=5$ and $y=12$.
\item If $r+s^2+v^3=12$, $dr/dt=4$, and $ds/dt=-3$, find $dv/dt$ when $r=3$ and $s=1$.
\item Coffee is draining from a canonical filter into a cylindrical coffeepot at the rate of $10\in^3/\min$.
a. How fast is the level in the pot rising when the coffee in the cone is $5\in$ deep?
b. How fast is the level in the cone falling then?
(picture)
\end{enumerate}

\end{document}
